|

### 2023-06-29 full-paper/paper.Rmd
paper: add finial version

date: "2023-05-27"
id: 1612

blind: true
---

@@

>>>>

date: "2023-06-29"
id: 1612

blind: false
---

@@

# Acknowledgements

This study was funded by Research Foundation of Chongqing University of Science
and Technology (project No. ckrc2021073) and the 111 project (Grant No. B13041),
The authors also thank the support from the Berkeley Education Alliance for
Research in Singapore (BEARS) for the Singapore-Berkeley Building Efficiency and
Sustainability in the Tropics (SinBerBEST) Program and thank Prof. Adrian Chong
(National University of Singapore) for his scientific input during epwshiftr
development.
